---
title: "Draft Quarto File"
author: "Adam"
format: html
---

```{r setup}
library(tidyverse)
library(here)
library(snakecase)
library(fs)

here::i_am("docs/learning.qmd")
source(here("R/functions.R"))
```

## for description document 
```{r}
usethis::use_package("dplyr")
usethis::use_package("stringr")
```

## Importing raw data

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  readr::read_csv(show_col_types = FALSE)
```

## Reading data with a function

```{r}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 100)

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

## Using map
```{r}
hr_files <- here("data-raw/nurses-stress/") |>
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_data <- hr_files |>
  map(read) |>
  list_rbind(names_to = "file_path_id")

hr_data
```

##exercise 18.5 
```{r}
#| eval: false
#| include: false
#' Read all `.csv.gz` files in the `stress/` folder into one data frame.
#'
#' @param filename The name of files in the sub-folders that we
#'    want to read in.
#'
#' @returns A single data frame/tibble.
#'
read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") |>
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files |>
    purrr::map(read) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all("HR.csv.gz")
read_all("IBI.csv.gz")
```
```{r}
read_all("HR.csv.gz")
read_all("IBI.csv.gz")
```
##Inspecting the data
```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data
```
```{r}
hr_data %>%
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) %>%
      str_remove("/stress/") %>%
      str_remove("/"),
    .before = file_path_id
  ) %>%
  select(-file_path_id)
```
##Convert ‘get ID’ code into a function
```{r}
get_participant_id <- function(data) {
  data_with_id <- data %>%
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) %>%
        stringr::str_remove("/stress/") %>%
        stringr::str_remove("/"),
      .before = file_path_id
    ) %>%
    dplyr::select(-file_path_id)

  return(data_with_id)
}
```
# How it will be used.
```{r}
get_participant_id(hr_data)
```
```{r}
print(survey_data)
```

## Working with across 
```{r}
hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id()
```

## working with across function
```{r}
hr_data %>%
  summarize(across(where(is.numeric), list(
    standardeviation = sd,
    mean = mean,
    median = median,
    min = min,
    max = max
  )))
```
```{r}
hr_data %>%
  summarize(across(hr, \(x)mean(x, na.rm = TRUE)))
```


## Working with dates
```{r}
hr_data %>%
  mutate(
    datetime = round_date(collection_datetime, unit = "minute"),
    .before = "collection_datetime"
  )
```

## Summarizing by groups 
```{r}
hr_data %>%
  mutate(
    collection_datetime = round_date(
      collection_datetime,
      unit = "minute"
    )
  ) %>%
  summarize(
    across(
      where(is.numeric),
      list(
        standardeviation = sd,
        mean = mean,
        median = median,
        min = min,
        max = max
      )
    ),
    .by = c(id, collection_datetime)
  )
```


```{r}
summarize_by_datetime <- function(data) {
  summarized_data <- data |>
    # Fill in below with the code we just wrote.
    mutate(
    collection_datetime = round_date(
      collection_datetime,
      unit = "minute"
    )
  ) %>%
  summarize(
    across(
      where(is.numeric),
      list(
        standardeviation = sd,
        mean = mean,
        median = median,
        min = min,
        max = max
      )
    ),
    .by = c(id, collection_datetime)
  )
  return(summarise_by_datetime(hr_data))
}
```
## Pivot longer

```{r}
```


```{r}
survey_data <- 
  here("data-raw/nurses-stress/survey-results.csv.gz") %>% 
  read()
survey_data
```

```{r}
survey_tidy <- survey_data %>% 
  mutate(date = mdy(date),
         start_datetime=as_datetime(paste(date, start_time)),
         end_datetime = as_datetime(paste(date, end_time)),
         datetime_id = start_datetime,
         .before =start_time) %>% 
select(-c(date,start_time,end_time,duration))
```

```{r}
survey_tidy %>% 
  select(id, datetime_id,start_datetime,end_datetime) %>% 
  pivot_longer(c(start_datetime, end_datetime))
```

```{r}
survey_tidy %>% 
  select(id, datetime_id,start_datetime,end_datetime) %>% 
  pivot_longer(c(start_datetime, end_datetime), names_to =NULL)
```

```{r}
survey_tidy %>% 
  select(id, datetime_id,start_datetime,end_datetime) %>% 
  pivot_longer(c(start_datetime, end_datetime), names_to =NULL, values_to ="collection_datetime")
```

```{r}
survey_tidy %>% 
  select(id, datetime_id,start_datetime,end_datetime) %>% 
  pivot_longer(c(start_datetime, end_datetime), names_to =NULL, values_to ="collection_datetime") %>% 
  group_by(pick(-collection_datetime)) %>% 
  complete(collection_datetime = seq(min(collection_datetime),max(collection_datetime), by = 60)) 
```
```{r}
survey_tidy %>% 
  select(id, datetime_id,start_datetime,end_datetime) %>% 
  pivot_longer(c(start_datetime, end_datetime), names_to =NULL, values_to ="collection_datetime") %>% 
  group_by(pick(-collection_datetime)) %>% 
  complete(collection_datetime = seq(min(collection_datetime),max(collection_datetime), by = 60)) %>% 
  ungroup()
```
## pivoted data made into function
```{r}
tidy_survey_dates <- function(data){
  tidied <- data %>% 
  mutate(date = mdy(date),
         start_datetime=as_datetime(paste(date, start_time)),
         end_datetime = as_datetime(paste(date, end_time)),
         datetime_id = start_datetime,
         .before =start_time) %>% 
  select(id, datetime_id,start_datetime,end_datetime)}
```

##pivoted data made into function survey_to_long
```{r}
survey_to_long <- function(data) {
  longer <- data |>
    dplyr::select(id, datetime_id, start_datetime, end_datetime) |>
    tidyr::pivot_longer(
      c(start_datetime, end_datetime),
      names_to = NULL,
      values_to = "collection_datetime"
    ) |>
    dplyr::group_by(dplyr::pick(-collection_datetime)) |>
    tidyr::complete(
      collection_datetime = seq(
        min(collection_datetime),
        max(collection_datetime),
        by = 60
      )
    ) |>
    dplyr::ungroup()
  return(longer)
}
```


```{r}
survey_tidy <- survey_data %>% 
  tidy_survey_dates() %>% 
  survey_to_long() 
  
```

```{r}
hr_data <- read_all("HR.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

ibi_data <- read_all("IBI.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

temp_data <- read_all("TEMP.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

bvp_data <- read_all("BVP.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

eda_data <- read_all("EDA.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()
```

```{r}
survey_tidy <- here::here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read() |>
  tidy_survey_dates()

survey_long <- survey_tidy |>
  survey_to_long()
```

```{r}
survey_long %>% 
  left_join(survey_tidy)

survey_tidy %>% 
  count(id,datetime_id) %>% 
  filter(n>1)

survey_long %>% 
  right_join(survey_tidy)

survey_long %>% 
  full_join(survey_tidy)

```
 ## joining survey and center data(hr_data)
```{r}
nurses_stress <- survey_long %>% 
  full_join(survey_tidy) %>% 
  full_join(hr_data)
  
nurses_stress %>% 
  arrange(id, collection_datetime) %>% 
  view()

nurses_stress
```
```{r}
nurses_stress <- survey_long %>%
  full_join(survey_tidy) %>%
  full_join(hr_data) %>%
  full_join(ibi_data) %>%
  full_join(temp_data) %>%
  full_join(bvp_data) %>%
  full_join(eda_data)

nurses_stress %>%
  arrange(id, collection_datetime)  

  nurses_stress
```
```
  
